Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2021-11-13 bbbq_article.tex
Move in vivo presentation of TMH-derived epitopes in T cells to SupMat and explain the rationale there

  \begin{subfigure}[t]{0.45\textwidth}
    \centering
    \caption{}
    \includegraphics[width=1.0\textwidth]{bbbq_article_issue_157/figure_2c.png}
    \label{fig:2c}
  \end{subfigure}  
  \hfill
  \begin{subfigure}[t]{0.45\textwidth}
    \centering
    \caption{}
    \includegraphics[width=1.0\textwidth]{bbbq_article_issue_157/figure_2d.png}
    \label{fig:2d}
  \end{subfigure}  
  \caption{
    \textbf{
      Robust prediction that TMH epitopes are presented \emph{in vivo}.
    }
    The percentage of epitopes for MHC-I and -II alleles 
    that overlap with TMHs that are presented
    \textbf{(A)} 
    Observed and predicted percentage of TMH-derived epitopes
    \textbf{(B)} 
    Observed and predicted percentage of TMH-derived epitopes,
    with a red linear regression line and 95\% confidence interval
    \textbf{(C)} 
    MHC ligands from the IEDB bind to TMH-derived epitopes.
    The numbers above the bars denotes the number of epitopes
    obtained using an MHC ligand assay
    \textbf{(D)} 
    T cells from the IEDB presnt TMH-derived epitopes.
    The numbers above the bars denotes the number of epitopes
    obtained using a T cell assay
  }
  \label{fig:elution}
\end{figure}

@@

>>>>

  \begin{subfigure}[t]{0.45\textwidth}
    \centering
    \caption{}
    \includegraphics[width=1.0\textwidth]{bbbq_article_issue_157/figure_2c.png}
    \label{fig:2c}
  \end{subfigure}

  \caption{
    \textbf{
      Robust prediction that TMH epitopes are presented \emph{in vivo}.
    }
    The percentage of epitopes for MHC-I and -II alleles 
    that overlap with TMHs that are presented
    \textbf{(A)} 
    Observed and predicted percentage of TMH-derived epitopes
    \textbf{(B)} 
    Observed and predicted percentage of TMH-derived epitopes,
    with a red linear regression line and 95\% confidence interval
    \textbf{(C)} 
    MHC ligands from the IEDB bind to TMH-derived epitopes.
    The numbers above the bars denotes the number of epitopes
    obtained using an MHC ligand assay
  }
  \label{fig:elution}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Presentation of TMH-derived epitopes \emph{in vivo}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Figure \ref{fig:elution_versus} shows the percentage of TMH-derived
epitopes as presented \emph{in vivo} in T cells. 
The data was obtained from the IEDB and includes only the MHC
alleles as used in this study. As there are many (especially class II)
MHC alleles, only a small percentage of the full IEDB data could be used.
Although this figure demonstrates that TMH-derived epitopes are presented
\emph{in vivo}, we excluded this figure from the main article, as these
protocols select epitopes in a non-random fashion (unlike the
MHC ligand assays, as presented in the main article).

\begin{figure}[!htbp]
  \centering
  \includegraphics[width=0.5\textwidth]{bbbq_article_issue_157/figure_2d.png}
  \caption{
    \textbf{
      T cells present TMH-derived epitopes \emph{in vivo}
    }
    The numbers above the bars denotes the number of epitopes
    found in the IEDB for the MHC alleles used in this study
  }
  \label{fig:elution_versus}
\end{figure}
